\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage[default]{lato}

% Remove page numbers
\pagestyle{empty}

% Custom colors
\definecolor{darkgray}{RGB}{64,64,64}
\definecolor{lightgray}{RGB}{128,128,128}

% Section formatting
\titleformat{\section}{\Large\bfseries\color{darkgray}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{20pt}{10pt}

% Header formatting - name/title left, details right
\newcommand{\header}[6]{
    \noindent
    \begin{minipage}[t]{0.6\textwidth}
        {\Huge\bfseries #1}
        
        \vspace{5pt}
        {\Large #2}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.35\textwidth}
        \raggedleft
        #3
        
        tel: #4
        
        #5
        
        #6
    \end{minipage}
    
    \vspace{20pt}
}

% Custom commands - fixed layout and indentation
\newcommand{\cventry}[5]{
    \noindent
    \begin{minipage}[t]{0.3\textwidth}
        \raggedright
        \textbf{#1}
        
        \textit{#2}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.7\textwidth}
        \raggedright
        \textit{#3}
        
        #4
        
        #5
    \end{minipage}
    
    \vspace{8pt}
}

\newcommand{\cveducation}[6]{
    \noindent
    \begin{minipage}[t]{0.3\textwidth}
        \raggedright
        \textbf{#1}
        
        \textit{#2}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.7\textwidth}
        \raggedright
        \textit{#3}
        
        #4
        
        #5
        
        #6
    \end{minipage}
    
    \vspace{8pt}
}

\begin{document}

% Header
\header{KENAN JASIM}{Senior Software Engineer}{73A St. Gabriels Rd, London, NW2 4DU}{07450167829}{kenan@kenanjasim.com}{www.kenanjasim.com}

% Profile Section
\section{PROFILE}
Experienced software engineer specialising in distributed cloud computing, open-source infrastructure tools and IoT platforms. Background in electronic engineering, graduating top of class from King's College London. Lead design and development of an IoT security platform providing automatic device registration and secured network communication. Extensive experience in infrastructure development (IaC), highly scalable application design utilising Kubernetes and API development. Proven to be a keen problem solver who is extremely quick to learn and apply new technologies. Highly effective and reliable team player, particularly in fast paced development environments.

% Work Experience Section
\section{WORK EXPERIENCE}

\cventry{Senior Software Engineer}{Apr 2025 - Present}{Safe Intelligence, 1 Lyric Square, London W6 0NB}{}{
Developed a platform focused on formal verification of machine learning models with applications in finance and object detection.
}

\cventry{Senior Software Engineer}{Jun 2022 - Apr 2025}{Crypto Quantique - Unit 304-5, 164-180 Union Street, London, SE1 0LH}{}{
Developed a distributed universal IoT platform focused on secure onboarding and device management.
\begin{itemize}[leftmargin=15pt, itemsep=2pt]
    \item Lead backend engineer developing a distributed system across Python (Django) and Golang with a MongoDB database deployed on AWS and Azure.
    \item Led the design, planning and implementation of new services, including creating features and user stories for said projects
    \item Improved the maintainability, performance and reliability of legacy codebases. Led initiatives to improve code quality in the team, such as onboarding projects into SonarQube.
    \item Designed and implemented functionality involving Embedded Linux, TPMs, MQTT, FOTA updates, HSMs and highly threaded virtual devices.
    \item Worked closely across teams to push for better infrastructure, cleaner architecture, better coding practices and standards.
    \item Took on the responsibility of onboarding, training and mentoring members of the team.
\end{itemize}
}

\cventry{Full-stack Software Engineer}{Oct 2020 – Jun 2022}{Konica Minolta - 90 Chancery Ln, Holborn, London}{}{
Full-stack engineer contributing to two Innovate UK funded projects focusing on cloud and industrial IoT orchestration.
\begin{itemize}[leftmargin=15pt, itemsep=2pt]
    \item Researched and developed a cloud native architecture for a cloud IoT platform which has the ability to detect and connect remote devices to cloud hosted virtual machines.
    \item Developed and implemented a network scanner, backend REST API, frontend GUI and command line. Utilised linux networking (VxLAN) and a VPN to allow device detection across physical networks.
    \item Developed a solution for remote device detection as part of an inter-department project providing box defect detection services.
\end{itemize}
}

\cventry{Hybrid Cloud Developer (Internship)}{Mar 2020 – Aug 2020}{Konica Minolta - 90 Chancery Ln, Holborn, London}{}{
Researched and prototyped cloud orchestration solutions as part of the global research and development team, contributing to a successful innovate UK application.
}

\cventry{Full Stack Developer/Electronic Engineer}{Mar 2019 – Oct 2019}{SiriusInsight.AI, 91 Waterloo Rd, South Bank, London, SE1 8SF}{}{
Contributed to the development of a maritime detection prototype providing data streams from camera feeds, mobile antennas and radar. The system was successfully deployed to a maritime light vessel as part of a proof of concept demonstration funded by EU Horizon.
}

\cventry{Teaching Assistant}{Sept 2019 – Dec 2019}{King's College London, Strand, London}{}{
Supported in the delivery of first-year undergraduate labs. Supervised workshops demonstrating circuit design, construction and experiment tracking. Supported students with feedback and troubleshooting.
}

\cventry{Refugee Casework Volunteer}{Jan 2019 - Jan 2021}{British Red Cross, 5 Berners Rd, Angel, London}{}{
Assist asylum seekers and refugees with issues such as asylum support, destitution support, general advice and family reunion.
}

% Education Section
\section{EDUCATION}

\cveducation{Certified Kubernetes Administrator}{Mar 2022 - Mar 2025}{Linux Foundation}{The Certified Kubernetes Administrator (CKA) certified the skills, knowledge, and competency to perform the responsibilities of Kubernetes administrators.}{}{}

\cveducation{BEng Electronic and Information Engineering (88\%)}{Sep 2017 – May 2020}{King's College London}{Degree - First class with honours}{Awards - John Oriel Prize (Top in exam) and Engineering Society Centenary Prize (Top in exam after 3 years)}{}

\cveducation{A-Levels and GCSEs}{Sep 2011 – Jul 2017}{St Margaret Ward}{A-levels - Biology - B, Computer Science – B, Mathematics – B.}{GCSEs - 11 GCSEs - 3A* 3A 5B (Maths - A*, English – B, Computer Science – A, Physics – A*)}{}

% Skills and Interests Section
\section{SKILLS AND INTERESTS}

\begin{minipage}[t]{0.48\textwidth}
\textbf{Technical Skills}

I pride myself in writing clean, maintainable and tested code. I am proficient in: Golang, Python, and Bash and have good experience developing in Typescript(React frontend) and C.

I am proficient in using Kubernetes, Docker, Ansible, Jenkins, Git and Terraform and have good experience with Openstack, AWS and Azure.

I am proficient in Linux and its networking stack and have experience with multiple SQL (PostgreSQL \& MariaDB) and NoSQL (MongoDB \& etcd) databases.
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
\textbf{Soft Skills}
\begin{itemize}[leftmargin=15pt, itemsep=2pt]
    \item Speak English (Native) and Arabic (Fluent)
    \item ASDAN (Working with Others, Improving own learning and Performance) \& ESB (English Speaking Board)
\end{itemize}

\textbf{Interests}
\begin{itemize}[leftmargin=15pt, itemsep=2pt]
    \item Snooker, football, running, bouldering, reading, cooking filmmaking, photography and video editing
\end{itemize}

\end{minipage}

\end{document} 